---
title: "Progress Memo"
subtitle: |
  | Final Project 
  | Data Visualization (STAT 302)
author: "Chelsea Nelson"
date: today
format:
  html:
    toc: true
    embed-resources: true
editor: 
  markdown: 
    wrap: 72
---

## Data source

```{r}
#| label: loading-packages
#| echo: false
#| message: false

library(tidyverse)
```

I will be using the Seoul Bike Sharing Demand Prediction dataset. [^1]
This dataset provides insights into the number of bikes rented per hour
for a full year from December 1st, 2017 to November 30th, 2018 in Seoul,
South Korea. This is alongside corresponding weather information to help
us see the relationship between bike sharing demand and weather
conditions. The dataset looks specifically at temperature, humidity,
windspeed, visibility, solar radiation, snowfall, and rainfall.

[^1]: This dataset was sourced from [Kaggle Seoul Bike Sharing Demand
    Prediction
    Dataset](https://www.kaggle.com/datasets/joebeachcapital/seoul-bike-sharing/data).

## Basic data description

```{r}
#| label: loading-dataset
#| message: false
#| echo: false

# loading dataset
seoulbike_data <- read_csv("data/SeoulBikeData.csv",  
                           locale = locale(encoding = "latin1"))

seoulbike_data %>% reactable::reactable()
 

```

In terms of observations there are 8760 observations, which is a
combination of every hour of every day for a full year. Additionally,
there are 14 variables in the original dataset, however I will add
another variable which will be a date-time variable. There is no
instance of missingness in my dataset.

```{r}
#| label: skimming_data 
#| echo: false

seoulbike_data %>% skimr::skim_without_charts() 
```

## Why this data

I choose this data, because I really love to see the usage of more
public transportation by people around the globe as we are in this era
of the rise of global warming and a need to assess different ways that
we has people can help to solve it. Additionally, I think it would be
interesting to see portray and showcase which factors play a larger role
in the collective decision to use or not use public transportation, such
bike sharing. I also think that this is a lot of data both from the
observation and variable point of view, thus I really want to challenge
myself to make great looking visualizations to really represent these
relationships between bike sharing and different types of weather
conditions.

## Visualization plan

Currently I plan to make a dashboard, with about 3 different pages where
in the first page it allows for the user to look at bike sharing numbers
to each weather condition separately, providing both a plot and a
correlation visualization. The second page will allow users to look at
multiple weather conditions and their relationship to bike sharing
numbers at once. Finally, I think I will allow for users to see how
different months or seasons compare to each other overall in terms of
bike sharing demands, whiles also highlighting the different factors
that play into this.

Additionally, within all of these, I will probably focus on the weather
conditions that correspond/correlate to bike sharing demands the most
after doing my own future research and correlation statistics on my
dataset.
